What do incoming university students believe about open science practices in

### 2021-03-09 analysis/Manuscript.Rmd

```{r, difference between norm & counternorm, eval = FALSE}

# select all columns that relate to norms & counternorms
diff <- df %>% select(c(id, ends_with("norm")))

means <- diff %>% 
  sapply(mean, na.rm = TRUE)

knitr::kable(means)

# select columns that relate to norms
norms <- df %>% select(c(id, ends_with("_norm")))

# select columns that relate to counternorms
cnorms <- df %>% select(c(id, ends_with("_cnorm")))

# breadcrumbs - pivot long

norm_long <- norms %>% 
  pivot_longer (cols = ends_with("norm"),
                names_to = "practice",
                values_to = "rating") 
  str_remove(norm_long, "_norm")

norm_wide <- diff %>% 
  pivot_wider(names_from = ends_with("_norm"),
              values_from = c(ends_with("_norm"), ends_with("_cnorm"))
)
```

>>>>

```{r, difference between norm and counternorm}

# select columns that relate to norms & pivot it long
norm_long <- df %>% 
  select(c(id, ends_with("_norm"))) %>% 
    pivot_longer (cols = ends_with("norm"),
                names_to = "practice",
                values_to = "norm rating")

# remove "_norm" from the practice variables
norm_long$practice = gsub(pattern = "_norm", replacement = "", x = norm_long$practice)

# select columns that relate to counternorms
cnorm_long <- df %>% 
  select(c(id, ends_with("_cnorm"))) %>% 
  pivot_longer (cols = ends_with("cnorm"),
                names_to = "practice",
                values_to = "cnorm rating")

# remove "_cnorm" from the practice variables
cnorm_long$practice = gsub(pattern = "_cnorm", replacement = "", x = cnorm_long$practice)

# join the norm and counternorm tibbles
norm_cnorm <- norm_long %>% inner_join(cnorm_long)

# create a `diff` variable that is the counternorm subtracted from the norm
norm_cnorm <- norm_cnorm %>% 
  mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
      dplyr::select(-(`id`)) # remove this now that I've confirmed it works

norm_means <- norm_cnorm %>% 
    dplyr::group_by(practice) %>%  
    summarise(norm_mean = mean(`norm rating`, na.rm = TRUE), 
              norm_sd = sd(`norm rating`, na.rm = TRUE), 
              cnorm_mean = mean(`cnorm rating`, na.rm = TRUE), 
              cnorm_sd = sd(`cnorm rating`, na.rm = TRUE), 
              diff_mean = mean(`diff`, na.rm = TRUE), 
              diff_sd = sd(`diff`, na.rm = TRUE)) %>% 
  ungroup()

# breadcrumb: I need to use papaja tables....
# pull means & sd into the same column with (sd) in parentheses
# headings should then be norm, counternorm, difference

knitr::kable(norm_means,
             caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
             digits = 2,
             align = c('lcccccc'))

# breadcrumbs: rename the practices so it's easier to read

# I don't need this...
# norm_means <- norm_cnorm %>% 
    # select(-id) %>% 
    # group_by(practice) %>%  
    # mutate(norm_mean = mean(`norm rating`, na.rm = TRUE)) %>% 
    # mutate(norm_sd = sd(`norm rating`, na.rm = TRUE)) %>% 
    # mutate(cnorm_mean = mean(`cnorm rating`, na.rm = TRUE)) %>% 
    # mutate(cnorm_sd = sd(`cnorm rating`, na.rm = TRUE)) %>% 
    # mutate(diff_mean = mean(`diff`, na.rm = TRUE)) %>% 
    # mutate(diff_sd = sd(`diff`, na.rm = TRUE))
